\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-16 evaluation.tex
typos

Modeling the Live Migration Table required \PDComment{waiting confirmation from Matt}. This case study is interesting because the development of the actual system and its \psharp environmental model occurred side-by-side. This is in contrast with the other two case studies discussed in this paper, where the modeling activity occurred independently and at a later stage of the development process.

Modeling Fabric required approximately 4-5 months. Although this is a significant amount of time, it is a one time effort activity. Our plan is to reuse the developed Fabric model for testing arbitrary user services built for the Azure Service Fabric system.

@@

We performed all experiments using the Windows PowerShell tool on a 2.50GHz Intel Core i5-4300U CPU with 8GB RAM running Windows 10 Pro 64-bit. We configured the engine to perform 100,000 iterations. The random seed for both schedulers was generated in each iteration using the \texttt{DateTime.Now.Millisecond} API which returns the current time in milliseconds. The PCT scheduler was further configured with a bug depth of 2 and a max number of scheduling steps to execute of 500. All reported times are in seconds.

>>>>

Modeling the Live Migration Table required \PDComment{waiting confirmation from
Matt}. The modeling effort was done in parallel with the development of the actual system. 
This is in contrast with the other two case studies discussed in this paper, where the modeling 
activity occurred independently and at a later stage of the development process.

Modeling Fabric required approximately 5 person months. Although this is a
significant amount of time, it is a one time effort (once per release). Our plan is to reuse the developed Fabric model 
for testing arbitrary user services built for the Azure Service Fabric system.

@@

We performed all experiments using the Windows PowerShell tool on a 2.50GHz Intel Core i5-4300U CPU with 8GB RAM running Windows 10 Pro 64-bit. We configured the engine to perform 100,000 iterations. The random seed for both schedulers was generated in each iteration using the \texttt{DateTime.Now.Millisecond} API which returns the current time in milliseconds. The PCT scheduler was further configured with a bug depth of 2 and a max number of scheduling steps of 500. All reported times are in seconds.

### 2015-09-16 experience.tex
typos

The Live Azure Table Migration (MigratingTable) is a library for \emph{transparently migrating} a data set between tables in an Azure Storage service \emph{while} an application is accessing this data set. This case study is interesting because its developers built the \psharp model of the system while developing the library to increase confidence in its implementation; indeed they discovered many bugs during this \emph{co-development} process (see Section~\ref{}). Another interesting aspect of this system is that it heavily uses the \texttt{async}/\texttt{await} primitives, which were not supported in the original \psharp runtime, and thus required us to extend \psharp with support for intra-machine concurrency (see Section~\ref{}). Finally, a lot of complex safety properties were written to test MigratingTable with \psharp, whereas the vNext model focused on a single liveness property.

@@

The \psharp testing goal was to ensure that when multiple application processes, implementing the \texttt{IChainTable} interface, issue read and write operations to their own MigratingTable instances with the same backend tables, the behavior complies with the specification of \texttt{IChainTable} for the combined \emph{input history}.

>>>>

The Live Azure Table Migration (MigratingTable) is a library for
\emph{transparently migrating} a data set between tables in an Azure Storage
service \emph{while} an application is accessing this data set. This case study
is interesting because its developers built the \psharp model of the system
while developing the library to increase confidence in its implementation;
indeed they discovered many bugs during this \emph{co-development} process (see
Section~\ref{}). Another interesting aspect of this system is that it heavily
uses the \texttt{async}/\texttt{await} primitives, which were not supported in
the original \psharp runtime, and thus required us to extend \psharp with
support for intra-machine concurrency (see Section~\ref{}). Finally, multiple 
complex safety properties were written to test MigratingTable with \psharp, 
whereas the vNext model focused on a single liveness property.

@@

The testing goal was to ensure that when multiple application processes, implementing the \texttt{IChainTable} interface, issue read and write operations to their own MigratingTable instances with the same backend tables, the behavior complies with the specification of \texttt{IChainTable} for the combined \emph{input history}.
